UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-10 files/paper/paper.tex
updates

\subsection{Adversarial Networks}
GANs are a class of generative models based on game theory in which a generator network competes against an adversary.
Given an image $I^C$, the generator is trained to produce an image to try and fool the discriminator, which is trained to distinguish be between distorted
and non-distorted underwater images. In the original GAN formulation, the goal is to solve the minimax problem: \newline

@@

@@

\subsection{Objective}
Normal GAN objective, then go into WGAN-GP. L1 weight as well.

@@

\subsubsection{Generator}

\subsubsection{Discriminator}

>>>>

\subsection{Adversarial Networks}
GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator network competes against an adversary.
Given an image $I^D$, the generator is trained to produce an image to try and fool the discriminator, which is trained to distinguish be between distorted
and non-distorted underwater images. In the original GAN formulation, the goal is to solve the minimax problem: \newline

@@

\noindent In this formulation, the discriminator is hypothesized as a classifier with a sigmoid cross entropy loss function,
which in practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
hypothesize a different loss function for the discriminator \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}.

In our work, we adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of
clipping network weights like in \cite{arjovsky2017wasserstein}, enforces the Lipschitz constraint by enforcing a soft constraint on the
gradient norm of the discriminator's output with respect to its input. 
Following \cite{gulrajani2017improved}, the new objective then becomes

\begin{equation}
\begin{aligned}
   L = \mathbb{E}_{I^D \sim p_{gen}(I^D)} [D(I^D)] - \mathbb{E} & _{I^C \sim p_{train}(I^C)} [D(I^C)] + \\
   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x}||_2 -1)^2 ]
\end{aligned}
\end{equation}

@@

\subsection{Image Gradient Difference Loss}

@@
